author: "Thomas Holm-Weber"
date: "2023-03-28"
output: html_document
title: "Bil code"
---
---


#Packagesinstall
```{r, echo=FALSE}

install.packages("tidyverse", repos = "http://cran.us.r-project.org")
install.packages("kableExtra")
install.packages("knitr")
install.packages("sjmisc")
```
#PackagesLibrary
```{r, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(kableExtra)
library(knitr)
library(sjmisc)
```


#Data Import Mac
```{r, echo=FALSE}
getwd()
setwd("/Users/thomasholm-weber/Desktop/bil/bil2/data")
bil = read_csv("bil.csv")
```

#Data Import PC
```{r}
getwd()
setwd("H:/PhD RH 2019 - 2022/Prj 4 BILACO/rbil/bil2/data")
bil = read_csv("bil.csv")
```

#Subsets disease & rename variables
```{r, echo=FALSE}
bil$disease = recode(bil$disease, "1" = "ba", "2" = "tof", "3" = "cc", "4" = "control")
bil$mm_for_estimation_of_cvp = recode(bil$mm_for_estimation_of_cvp, "1" = "Normal")
bil$color_for_evaluation_of_ar = recode(bil$color_for_evaluation_of_ar, "1" = "No Aortic Regurgitation")
bil$pr = recode(bil$color_for_estimation_of_pr, "1" = "None", "2" = "Mild", "3" = "Moderat ", "4" = "Severe")
bil$mv_color_interrogation_for = recode(bil$mv_color_interrogation_for, "1" = "No Mitral Valve Regurgitation", "2" = "Mild Mitral Valve Regurgitation")
bil$congenital_anatomy = recode(bil$congenital_anatomy, "1" = "ToF", "2" = "ToF PA", "3" = "ToF near PA", "4" = "ToF PA w/ MAPCA")
bil$sex = recode(bil$sex, "1" = "M", "2" = "F")
bil$shunt = recode(bil$shunt, "1" = "Yes", "2" = "No")
bil$shunt_in_months = recode(bil$shunt_in_months, "0" = "-", "3" = "3", "18" = "18", "8" = "8")
bil$pink_or_blue = recode(bil$pink_or_blue, "1" = "Pink", "2" = "Blue")
bil$sat_newborn = recode(bil$sat_newborn, "1" = "96-100", "2" = "91-95", "3" = "86-90", "4" = "81-85", "5" =  "76-80", "6" = "70-75", "7" = "< 70", "8" = "NA")
bil$prolonged_pleura_effusion = recode(bil$prolonged_pleura_effusion, "1" = "Yes", "2" = "No")
bil$td_tortousity_asfac = recode(bil$td_tortousity_agreed, "1" = "None", "2" = "Mild", "3" = "Moderate", "4" = "Severe")
bil$revalved = recode(bil$revalved, "1" = "Yes", "0" = "No")

bil$wz =  paste(bil$weight, "(", bil$weight_z_score, ")", sep ="")
bil$hz =  paste(bil$height, "(", bil$height_z_score, ")", sep ="")
bil$bmiz = paste(bil$bmi, "(", bil$bmi_z_score, ")", sep ="")

glimpse(bil$shunt_in_months)


##lrate_diff
bil$lrate_diff = bil$lrate - bil$lrate_2

##rname cols
bil = bil %>% rename(
    ID = fp_nr,
    Type = mritype_agreed,
    "Rate 1" = lrate,
    "Rate 2" = lrate_2,
    Pressure = lpressure,
    PR = pr,
    CVP = mm_for_estimation_of_cvp,
    TAPSE = mm_lateral_tv_annulus_for,
    EF = ef
)

ba = bil %>% filter(disease=="ba")
tof = bil %>% filter(disease=="tof")  %>% slice(-8)
cc = bil %>% filter(disease=="cc")
control = bil %>% filter(disease=="control") %>% slice(-4)

tof$ID = recode(tof$ID,
                   "9" = "A", 
                   "13" = "B", 
                   "14" = "C", 
                   "15" = "D", 
                   "16" = "E", 
                   "17" = "F", 
                   "18" = "G",
                   "19" = "H", 
                   "24" = "I")

control$ID = recode(control$ID,
                   "50" = "I", 
                   "51" = "II", 
                   "52" = "III", 
                   "54" = "IV", 
                   "55" = "V", 
                   "56" = "VI", 
                   "57" = "VII",
                   "58" = "VIII", 
                   "59" = "IX",
                   "60" = "X")

```


#ToF Table1
```{r}
##Table 1
toft1 <- tof %>% 
  select(ID,
         age_at_doi,
         wz,
         hz,
         bmiz,
         PR,
         CVP,
        TAPSE2,
    EF) %>% arrange(ID)


toft1 = toft1 %>% 
  rename(
    "Age" = age_at_doi,
    "BMI, kg/m2" = bmiz,
    "Height, cm" = hz,
    "Weight, kg" = wz,
    "TAPSE" = TAPSE2)


tof1latex = kbl(toft1, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Baseline characteristics - ToF Patients",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  kable_styling(position = "center") %>%
  add_header_above(c(" " = 5, "Echocardiography" = 4))


cat(tof1latex)
```

#Table1 ToF + controls minus Echo
```{r}

#Means
meanse <- function(x, ...){
  mean1 <-   signif(round(mean(x, na.rm=T),2), 2)   #calculate mean and round
  se1 <- signif(round(sd(x, na.rm=T), 2),1) # std error - round adding zeros
  out <- paste(mean1, "$\\pm$", se1)  # paste together mean plus/minus and standard error
  if (str_detect(out,"NA")) {out="NA"}   # if missing do not add plusminus
  return(out)
}

#Categorical values
summarize_categorical_variable <- function(data, variable_name) {
  summary <- data %>%
    mutate({{variable_name}} := factor({{variable_name}})) %>%
    group_by({{variable_name}}) %>%
    summarize(
      Count = n()
    ) %>%
    ungroup()

  total_count <- sum(summary$Count)
  percentages <- (summary$Count / total_count) * 100

  summary_text <- paste(
    summary$Count,
    "(",
    round(percentages, 0),
    "x)/",
    total_count - summary$Count,
    "(",
    round(100 - percentages, 0),
    "x)",
    sep = ""
  )

  return(summary_text)
}

csex = summarize_categorical_variable(control, sex)

tsex = summarize_categorical_variable(tof, sex)

#cstest

## Create a data frame with your data
data <- data.frame(
  Group = c("Group1", "Group2"),
  Male = c(4, 5),
  Female = c(5, 5)
)

# Create a contingency table
contingency_table <- matrix(c(data$Male, data$Female), ncol = 2)

# Perform Fisher's Exact Test
fisher_result <- fisher.test(contingency_table)

sexcstest = (fisher_result)$p.value


Sex = c(csex[1], tsex[1], sexcstest)

Sex

Age = c(meanse(control$age_at_doi), 
        meanse(tof$age_at_doi), 
        sprintf("%.3f",t.test(control$age_at_doi,tof$age_at_doi, na.rm= T)$p.value))

Age

Weight = c(meanse(control$weight_z_score),
           meanse(tof$weight_z_score), 
           sprintf("%.3f",t.test(control$weight_z_score,tof$weight_z_score, na.rm= T)$p.value))

Weight
  
Height = c(meanse(control$height_z_score),
           meanse(tof$height_z_score),
          sprintf("%.3f",t.test(control$height_z_score,tof$height_z_score, na.rm= T)$p.value))

Height  

BMI = c(meanse(control$bmi_z_score),
           meanse(tof$bmi_z_score),
          sprintf("%.3f",t.test(control$bmi_z_score,tof$bmi_z_score, na.rm= T)$p.value))

BMI
  
T1tibble = tibble(Sex, Age, Height, Weight, BMI) %>% rotate_df() 

colnames(T1tibble) = c("Controls (n = 10)","Tetralogy of Fallot (n = 9)", "p-value")
rownames(T1tibble) = c("Sex (male/female), n(xx)", "Age (years)", "Weight", "Height", "BMI")

T1tibble



T1latex = kbl(T1tibble, "latex",
              booktabs = T, 
              digits = 2,
              align = c('r', 'r'),
              caption = "Table 1",
              linesep = "", 
              escape = FALSE) %>%
  kable_classic_2 

cat(T1latex)
```

#Echo table
```{r}
tof$TAPSE2 = paste(tof$TAPSE, "(", tof$tapse_z_score, ")", sep = "")

echot <- tof %>% 
  select(ID,
         CVP,
         TAPSE2,
         PR,
         rv_fac,
         rv_ls,
         lv_gls_average,
        EF) %>% arrange(ID) 

echot = echot %>% rename(
    "FAC" =rv_fac,
    "LS" = rv_ls,
    "GLS" = lv_gls_average,
    "TAPSE" = TAPSE2)

echolatex = kbl(echot, "latex",
              booktabs = T, 
              digits = 2,
              align = c('r', 'r'),
              caption = "Echocardiography",
              linesep = "", 
              escape = FALSE) %>% add_header_above(c(" " = 2, "Right Ventricle" = 4, "Left Ventricle" = 2)) %>%
  kable_classic_2 

cat(echolatex)
```



#Surgical history
```{r}
##Surgical hx
tofhx = tof %>% 
  select(ID,
         age_at_doi,
         sex,
         congenital_anatomy,
         sat_newborn,
         shunt_in_months,
         age_at_repair_months,
         repair_type,
         revalved,
         years_with_pr
         ) %>% arrange(ID)

tofhx = tofhx %>% 
  rename(
    "Sex" = sex,
    "Age" = age_at_doi,
    "Anatomy" = congenital_anatomy,
    "SAT (%)" = sat_newborn,
    "Shunted" = shunt_in_months,
    "Age" = age_at_repair_months,
    "Type" = repair_type,
    "Revalved" = revalved,
    "PR" = years_with_pr
  )


tofhxlatex = kbl(tofhx, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Surgical History",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 3, "Pre repair" = 3, "Repair" = 2, "Post repair" = 2))

cat(tofhxlatex)

#incl mri
tofhxmri = tof %>% 
  select(ID,
         age_at_doi,
         sex,
         congenital_anatomy,
         sat_newborn,
         shunt_in_months,
         age_at_repair_months,
         repair_type,
         revalved,
         years_with_pr,
        Type,
        td_tortousity_asfac,
        td_diameter_agreed,
               ) %>% arrange(ID)

tofhxmri = tofhxmri %>% 
  rename(
    "Age" = age_at_doi,
    "Sex" = sex,
    "Anatomy" = congenital_anatomy,
    "SAT (%)" = sat_newborn,
    "Shunted" = shunt_in_months,
    "Age " = age_at_repair_months,
    "Repair" = repair_type,
    "Revalved" = revalved,
    "PR" = years_with_pr,
     "Tortousity" = td_tortousity_asfac,
    "ø" = td_diameter_agreed)


tofhxmrilatex = kbl(tofhxmri, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Surgical History",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 3, "Pre repair" = 3, "Repair" = 2, "Post repair" = 2, "MRI findings" = 3))

cat(tofhxmrilatex)
```


#BloodtestsToF
```{r}
tofbt = tof %>% 
  select(86:89,
         91:104)


tofbt= tofbt %>% 
  rename(
    "Hemoglobin (mmol/L)" = 1,
    "Leucocytes (10^9/L)" = 2,
    "Lymphocytes (10^9/L)" = 3,
    "Platelets (10^9/L)" = 4,
    "Potassium (mmol/L)" = 5,
    "Sodium (mmol/L)" = 6,
    "Creatinin (μmol/l)" = 7,
    "Albumin (g/L)" = 8,
    "INR " = 9, 
    "ALAT (U/L)" = 10,
    "Bilirubin (μmol/l)" = 11,
    "Cholesterol (mmol/L)" = 12,
    "HDL (mmol/L)" = 13,
    "LDL (mmol/L)" = 14,
    "Glucose (mmol/L)" = 15,
    "CRP (mg/L)" = 16,
    "IgG (kU/L)" = 17,
    "IgE (kU/L)" = 18) 

#Transpose
transtofbt = tofbt %>% rotate_df() 

transtofbt = transtofbt %>% 
              rename(
                "A" = V1,
                "C" = V2,
                "D" = V3,
                "E" = V4,
                "F" = V5, 
                "H" = V6,
                "B" = V7,
                "I" = V8,
                "G" = V9)

transtofbt = transtofbt %>% 
              select(A,B,C,D,E,F,G,H,I)

tofbtlat = kbl(transtofbt, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Blood tests results ToF",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 

cat(tofbtlat)
```

#BloodtestsControls
```{r}
conbt = control %>% 
  select(86:89,
         91:104)

conbt= conbt %>% 
  rename(
     "Hemoglobin (mmol/L)" = 1,
    "Leucocytes (10^9/L)" = 2,
    "Lymphocytes (10^9/L)" = 3,
    "Platelets (10^9/L)" = 4,
    "Potassium (mmol/L)" = 5,
    "Sodium (mmol/L)" = 6,
    "Creatinin (μmol/l)" = 7,
    "Albumin (g/L)" = 8,
    "INR " = 9, 
    "ALAT (U/L)" = 10,
    "Bilirubin (μmol/l)" = 11,
    "Cholesterol (mmol/L)" = 12,
    "HDL (mmol/L)" = 13,
    "LDL (mmol/L)" = 14,
    "Glucose (mmol/L)" = 15,
    "CRP (mg/L)" = 16,
    "IgG (kU/L)" = 17,
    "IgE (kU/L)" = 18) 

#Transpose
transconbt = conbt %>% rotate_df() 

transconbt = transconbt %>% 
              rename(
                "I" = V1,
                "II" = V2,
                "III" = V3,
                "IV" = V4,
                "V" = V5, 
                "VI" = V6,
                "VII" = V7,
                "VIII" = V8,
                "IX" = V9,
                "X" =V10)



conbtlat = kbl(transconbt, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Blood tests results Controls",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 

cat(conbtlat)

mean(control$bmi_z_score, na.rm = T)

t.test(tof$bmi_z_score,control$bmi_z_score)
sd(tof$bmi_z_score)
sd(control$bmi_z_score, na.rm = T)

t.test(tof$height_z_score,control$height_z_score)
t.test(tof$weight_z_score,control$weight_z_score)
```




# Control vs ToF group
```{r}
#age
meanagecontrol = mean(control$age_at_doi)
sdagecontrol = sd(control$age_at_doi)


meanagetof = mean(tof$age_at_doi)
sdagetof = sd(tof$age_at_doi)

agettest = t.test(control$age_at_doi, tof$age_at_doi)

agettest

#TD
meantdcon = mean(control$td_diameter_agreed, na.rm = T)
sdtdcon = sd(control$td_diameter_agreed, na.rm = T)
meantdtof = mean(tof$td_diameter_agreed, na.rm = T)
sdtdtof = sd(tof$td_diameter_agreed, na.rm = T)

meantdcon
meantdtof
sdtdcon
sdtdtof


TDttest = t.test(control$td_diameter_agreed,tof$td_diameter_agreed)

TDttest

#Lymphscore
lscorettest = t.test(control$mritype_t, tof$Type)

lscorettest


#Coefiecient of varians
cvdiacons = (sd(control$td_diameter_s, na.rm = T))/(mean(control$td_diameter_s, na.rm = T))
cvdiacont = (sd(control$td_diameter, na.rm = T))/(mean(control$td_diameter, na.rm = T))

cvdiatofs = (sd(tof$td_diameter_s, na.rm = T))/(mean(tof$td_diameter_s, na.rm = T))
cvdiatoft = (sd(tof$td_diameter, na.rm = T))/(mean(tof$td_diameter, na.rm = T))


cvdiacons
cvdiacont
cvdiatofs
cvdiatoft

tof$diffdiatof = tof$td_diameter-tof$td_diameter_s
control$diffdiacon = control$td_diameter-control$td_diameter_s


tofdiadiff = tof %>%
            select(ID, diffdiatof)  %>%
            arrange(ID)
    
condiadiff = control %>%
            select(ID, diffdiacon)  %>%
            arrange(ID)

glimpse(tof$td_tortousity_agreed)
glimpse(control$td_tortousity_agreed)

toftordiff = tof %>%
            select(ID, td_tortousity_agreed)  %>%
            arrange(ID)
    
condtoriff = control %>%
            select(ID, td_tortousity_agreed)  %>%
            arrange(ID)

```

#Fibroscan table
```{r}
fibro <- tof %>% 
  select(ID,
         c(108:110)) %>% arrange(ID)

fibro = fibro %>% 
  rename(
    "FibroScan (kPa)" = fibroscan,
    "CAP score" = cap,
    "Interquartil range" = iqr
  )

fibrolat = kbl(fibro, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Fibroscan results - ToF patients",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2

cat(fibrolat)
```


#tofresultsMRI+NIRF
```{r}
tofresults <- tof %>% 
  select(
    ID,
    Type,
    td_tortousity_asfac,
    td_diameter_agreed,
    "Rate 1",
    "Rate 2",
    velo_1,
    velo_2,
    Pressure) %>% arrange(ID)

tofresults = tofresults %>% 
  rename(
    "R1" = "Rate 1",
    "R2" = "Rate 2",
    "P1" = Pressure,
    "V1" = velo_1,
    "V2" = velo_2,
    "Tortousity" = td_tortousity_asfac,
    "ø" = td_diameter_agreed)


toflatex = kbl(tofresults, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Lymphatic parameter results - ToF Patients",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 2, "Thoracuc duct" = 2, "Rate (/min)" = 2, "Velocity (cm/s)" = 2, "Pressure (mmHg)" = 1, " " = 5)) %>%
  add_header_above(c(" " = 1, "MRI" = 3, "NIRF" = 5)) 


cat(toflatex)

```

#tofresultsnirf
```{r}
tofnirf = tof %>% 
  select(
    ID,
    "Rate 1",
    velo_1,
    Pressure,
    "Rate 2",
    velo_2) %>% arrange(ID)

tofnirf = tofnirf %>% 
  rename(
    "Rate (/min)1" = "Rate 1",
    "Rate (/min)2" = "Rate 2",
    "Pressure (mmHg)" = Pressure,
    "Velocity (cm/s)1" = velo_1,
    "Velocity (cm/s)2" = velo_2)


tofnirflatex = kbl(tofnirf, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Lymphatic Near-infrared flourescence imaging results",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 1, "Sequence 1" = 2, "Sequence 2" = 1, "Sequence 3" = 2))


cat(tofnirflatex)

R1 = mean(tof$`Rate 1`, na.rm=T)
R1
V1 = mean(tof$velo_1, na.rm=T)
V1
LP = mean(tof$Pressure, na.rm=T)
LP
R2 = mean(tof$`Rate 2`, na.rm=T)
R2
V2 = mean(tof$velo_2, na.rm=T)
V2
```

#tofresultsmri
```{r}
tofresultsmri <- tof %>% 
  select(
    ID,
    Type,
    td_tortousity_asfac,
    td_diameter_agreed
    ) %>% arrange(ID)

tofresultsmri = tofresultsmri %>% 
  rename(
    "Tortousity" = td_tortousity_asfac,
    "Diameter" = td_diameter_agreed)


toflatexmri = kbl(tofresultsmri, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "Lymphatic MRI results",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 2, "Thoracuc duct" = 2)) 


cat(toflatexmri)
```




#MRI3 characteristics
```{r}
mr3 = tof %>% filter(Type=="3")

mr3t = mr3 %>%
  select(ID,
         congenital_anatomy,
         sat_newborn,
         shunt_in_months,
         age_at_repair_months,
         repair_type,
         prolonged_pleura_effusion,
         years_with_pr,
         td_tortousity_asfac,
         td_diameter) %>% arrange(ID)

mr3t = mr3t %>% 
  rename(
    "Anatomy" = congenital_anatomy,
    "Tortousity" = td_tortousity_asfac,
    "SAT" = sat_newborn,
    "Shunted" = shunt_in_months,
    "Age" = age_at_repair_months,
    "Type" = repair_type,
    "Complications" = prolonged_pleura_effusion,
    "PR" = years_with_pr,
    "ø" = td_diameter
  )


mr3t = kbl(mr3t, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "MRI type 3 characteristics",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 1, "Pre repair" = 3, "Repair" = 2, "Post repair" = 4)) %>%
  kable_styling(position = "center")

cat(mr3t)

mr3t2 =  mr3 %>%
  select(ID,
         congenital_anatomy,
         sat_newborn,
         shunt_in_months,
         age_at_repair_months,
         repair_type,
         years_with_pr,
         td_tortousity_asfac,
         td_diameter) %>% arrange(ID)

mr3t2 = mr3t2 %>% 
  rename(
    "Anatomy" = congenital_anatomy,
    "Tortousity" = td_tortousity_asfac,
    "SAT (%)" = sat_newborn,
    "Shunted (months)" = shunt_in_months,
    "Age (months)" = age_at_repair_months,
    "Type" = repair_type,
    "PR (years)" = years_with_pr,
    "ø (mm)" = td_diameter
  )

mr3t2 = kbl(mr3t2, "latex",
    booktabs = T, 
    digits = 1, 
    caption = "MRI type 3 characteristics",
    linesep = "",
    escape = FALSE) %>%
  kable_classic_2 %>%
  add_header_above(c(" " = 1, "Pre repair" = 3, "Repair" = 2, "Post repair" = 3))  %>%
  kable_styling(position = "center")

cat(mr3t2)
```


#correlationstof
```{r}
## TD tortousity to MRI
correlationtdtmri <- tof %>%
  summarize(correlationtdtmri = cor(Type, td_tortousity, use = "complete.obs", method = "pearson"))

print(correlationtdtmri)

## TD diameter to MRI¨
correlationtddmri <- tof %>%
  summarize(correlationtddmri = cor(Type, td_diameter, use = "complete.obs", method = "pearson"))

print(correlationtddmri)

## Lymph Rate to MRI
correlationlr1mri <- tof %>%
  summarize(correlationlr1mri = cor(Type, `Rate 1`, use = "complete.obs", method = "pearson"))

print(correlationlr1mri)

## Lymph Rate 2 to MRI
correlationlr2mri <- tof %>%
  summarize(correlationlr1mri = cor(Type, `Rate 2`, use = "complete.obs", method = "pearson"))

print(correlationlr2mri)

## Lymph Rate change to MRI
correlationlrdiffmri <- tof %>%
  summarize(correlationlr1mri = cor(Type, lrate_diff, use = "complete.obs", method = "pearson"))

print(correlationlrdiffmri)

## Lymph velocity 1 to MRI
correlationv1mri <- tof %>%
  summarize(correlationv1mri = cor(Type, velo_1, use = "complete.obs", method = "pearson"))

print(correlationv1mri)

## Lymph velocity 2 to MRI
correlationv2mri <- tof %>%
  summarize(correlationv2mri = cor(Type, velo_2, use = "complete.obs", method = "pearson"))

print(correlationv2mri)

## Lymph Pressure to MRI
correlationlpmri <- tof %>%
  summarize(correlationlpmri = cor(Type, Pressure, use = "complete.obs", method = "pearson"))

print(correlationlpmri)

## PR to MRI
correlationprmri <- tof %>%
  summarize(correlationpr1mri = cor(Type, color_for_estimation_of_pr, use = "complete.obs", method = "pearson"))

print(correlationprmri)

## Tapse to MRI
correlationtapsemri <- tof %>%
  summarize(correlationtapsemri = cor(Type, TAPSE, use = "complete.obs", method = "pearson"))

print(correlationtapsemri)

## Years PR to MRI
correlationyprmri <- tof %>%
  summarize(correlationyprmri = cor(Type, `PR (years)`, use = "complete.obs"), method = "pearson")

print(correlationyprmri)

```


#Non-participants vs participants
```{r}
##Sex
## Create a data frame with your data
datafish <- data.frame(
  Group = c("Group1", "Group2"),
  Male = c(4, 11),
  Female = c(5, 19)
)

# Create a contingency table
contingency_tablefish <- matrix(c(datafish$Male, datafish$Female), ncol = 2)

# Perform Fisher's Exact Test
fisher_resultfish <- fisher.test(contingency_tablefish)

sexcstestfish = (fisher_resultfish)$p.value

sexcstestfish

##Shunt
## Create a data frame with your data
datashunt <- data.frame(
  Group = c("Group1", "Group2"),
  Male = c(3, 5),
  Female = c(6, 25)
)

# Create a contingency table
contingency_tableshunt <- matrix(c(datashunt$Male, datashunt$Female), ncol = 2)

# Perform Fisher's Exact Test
fisher_resultshunt <- fisher.test(contingency_tableshunt)

sexcstestshunt = (fisher_resultshunt)$p.value

sexcstestshunt



##TAP
## Create a data frame with your data
datatap <- data.frame(
  Group = c("Group1", "Group2"),
  Male = c(7, 16),
  Female = c(2, 14)
)

# Create a contingency table
contingency_tabletap <- matrix(c(datatap$Male, datatap$Female), ncol = 2)

# Perform Fisher's Exact Test
fisher_resulttap <- fisher.test(contingency_tabletap)

sexcstesttap = (fisher_resulttap)$p.value

sexcstesttap


#Contegra graft
## Create a data frame with your data
dataconte <- data.frame(
  Group = c("Group1", "Group2"),
  Male = c(2, 5),
  Female = c(7, 25)
)

# Create a contingency table
contingency_tableconte <- matrix(c(dataconte$Male, dataconte$Female), ncol = 2)

# Perform Fisher's Exact Test
fisher_resultconte <- fisher.test(contingency_tableconte)

sexcstestconte = (fisher_resultconte)$p.value

sexcstestconte

#valve
## Create a data frame with your data
datavalve <- data.frame(
  Group = c("Group1", "Group2"),
  Male = c(0, 5),
  Female = c(9, 25)
)

# Create a contingency table
contingency_tablevalve <- matrix(c(datavalve$Male, datavalve$Female), ncol = 2)

# Perform Fisher's Exact Test
fisher_resultvalve <- fisher.test(contingency_tablevalve)

sexcstestvalve = (fisher_resultvalve)$p.value

sexcstestvalve

```



